Enhancement of SDR in Thessaloniki

### 2024-01-16 GHI_enh_04_investigate.tex
Commit 2024-01-16 13:14

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\begin{verbatim}
2024-01-16 09:48:38.4 athan@sagan GHI_enh_04_investigate.R 0.000095 mins
\end{verbatim}

>>>>

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Loading required package: stringr
\end{verbatim}

\begin{verbatim}
Run previous step: ./GHI_enh_03_process.R
\end{verbatim}

\begin{verbatim}

Attaching package: 'timetk'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:data.table':

    :=
\end{verbatim}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

\begin{verbatim}

Call:
stats::lm(formula = .formula, data = df)

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09

2024-01-16 10:20:53.2 athan@sagan GHI_enh_03_process.R 0.513138 mins
\end{verbatim}

\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\begin{verbatim}
2024-01-16 10:20:53.5 athan@sagan GHI_enh_03_process.R 0.000111 mins
\end{verbatim}
